Dynein project log

### 2017-09-30 thesis_stuff/thesis_stuff.tex
mini commit.

>>>>

Yildiz found that processivity and velocity are inversely related. This means that the MT-bound to unbound ratio is related to how far the motor can walk. Thus, tuning k_b and k_ub may be a way to alter dynein processivity.\\

A ring domain can be substituted with another protein and still walks, so ring-ring interactions aren't necessary for motion, either.\\

This result means that stalk registry changes aren't necessary for MT unbinding.\\

Abolishing linker swing by making weird constructs inhibits stepping when the linked head is mutated, but not when the unlinked head is muated.\\

There's a better stall-force measurement here than in other assays.\\
